Structured Versus Decorated Cospans

### 2022-03-05 ResponseToReviews.tex

{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.}

\item p. 9, ingredients for constructing a double functor of decorated cospan double categories.

Does the natural transformation $\theta$: EF $\Rightarrow$ F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see 
where in 
the following proofs that assumption is used.

{\color{blue}{Kenny: I think they are correct in that we don't use this extra assumption.}}

@@

\item p. 21, definition of F: Set $\to$ Cat

The use f, g for vertex/edge maps is opposite of the convention used on the previous page. I suggest that the same convention be used for both the 
decorated and structured approach to constructing open graphs.

{\chris I don't think I understand this, anyone else?}

{\color{blue}{Kenny: I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}}

@@

{\john
I don't want to bust up the examples and put some in sections 2 and 3. Anyone who wants examples can easily find them all in Section 6, we mention 
this section in the introduction (and perhaps should advertise it more there), and it's hard to analyze the examples without having all the theory in 
hand.}

{\chris Fourth review starts here}
\item Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” 
section.

{\chris I would be happy to add this to conventions, but I cannot seem to find gf anywhere in the paper. Anyone else?}

{\color{blue}{Kenny: They might not mean $gf$ specifically, but there are many instances where we don't use a $\circ$ for functional composition, e.g. when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21. Do we want to use a $\circ$ or not?}}

@@

{\chris Maybe just specify in the statement of 2.1, definitely keep $\in$ sign in all diagrams below!}

\item Proof of theorem 2.1: You should probably at least handwave that the cartesian liftings really are cartesian liftings. (No doubt it’s easy, but 
this 
is a classic sort of spot where errors can hide)

\item On page 9 during the construction of H, I would appreciate a sentence giving some intuition for the functor E, at this point I’m confused about 
its 
role.

{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. $F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if that makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}

### 2022-03-07 ResponseToReviews.tex

{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.}

\item p. 9, ingredients for constructing a double functor of decorated cospan double categories.

Does the natural transformation $\theta$: EF $\Rightarrow$ F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see 
where in 
the following proofs that assumption is used.

{\kenny I think they are correct in that we don't use this extra assumption.}

@@

\item p. 21, definition of F: Set $\to$ Cat

The use f, g for vertex/edge maps is opposite of the convention used on the previous page. I suggest that the same convention be used for both the 
decorated and structured approach to constructing open graphs.

{\chris I don't think I understand this, anyone else?}

{\kenny I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}

{\john That sounds plausible.  Unless there's a damn good reason let's use $f$ as a map for vertices and $g$ as a map for edges, since ``vertices come before edges'' - morally the first are 0-cells, the second are 1-cells.}

### 2022-03-07 cospans_new.tex
added a comment to "Response", made some changes in cospans_new.tex

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/6/29 - second arxiv version

@@

where the decoration morphism $\lH(\tau)$ is defined as follows.  Thinking of $\tau$ as a natural transformation \cref{eq:taunattransf},
in the same style of notation $\lH(\tau)$ is given by

@@

@@

The square at right commutes strictly because $\theta$ is a natural isomorphism.   \iffalse Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.  However, the following result suffices for the application in \cref{subsec:petrirates}. \fi

@@

Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing 
functors, and the induced fiberwise monoidal structure is cocartesian. Explicitly, regarding the last point, the lax monoidal 
pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$ given 
by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal. We here ask that the induced pseudofunctor $F\maps \A\to\SMC$ factors through 
$\Rex$, namely that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/07 - dealing with referee's comments

@@

where the decoration morphism $\lH(\tau)$ is defined as follows.  Treating $\tau$ as a natural transformation as in \cref{eq:taunattransf}, $\lH(\tau)$ is given by

@@

The square at right commutes strictly because $\theta$ is a natural isomorphism.

@@

   \iffalse Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.  However, the following result suffices for the application in \cref{subsec:petrirates}. \fi

@@

Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing functors, and the induced fiberwise monoidal structure is cocartesian. Regarding the last point: the lax monoidal pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ given by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal, and we ask that the resulting pseudofunctor $F\maps \A \to \SMC$ factors through $\Rex$, so that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
